Quality measure notes

### 2021-08-18 StateOfPractice/Ao-Report/12Background.tex
MI report - updated ch 1 and more
MI report - update ch 2

In this section, we introduce the relevant software categories (Section \ref{sec_software_categories}). We also cover the software quality definitions (Section \ref{sec_software_quality}) and an overview of the Analytic Hierarchy Process (AHP) (Section \ref{sec_AHP}).

@@

\section{Software Categories}
\label{sec_software_categories}
We target specific software categories to narrow down the scope when selecting software packages for measuring. In this section, we discuss three common software categories: Open source software (OSS), freeware, and commercial software.

@@

	\item \textbf{Correctness \& Verifiability} A program is correct if it behaves according to its stated. Verifiability is the extent to which a set of tests can be written and executed, to demonstrate that the delivered system meets the specification \cite{GhezziEtAl2003}.

@@

For a project with $ m $ criteria, we can use an $m\times m$ matrix $A$ to record the relative importance between factors. By pairwise compare criterion $i$ and criterion $j$, the value of $A_{ij}$ is decided as follows, and the value of $A_{ji}$ is $1/A_{ij}$ \cite{Saaty1990},
\begin{itemize}
	\item $A_{ij} = 1$ if criterion $i$ and criterion $j$ are equally important;
	\item $A_{ij} = 9$ if criterion $i$ is extremely more important than criterion $j$;
	\item $A_{ij}$ equals to an integer value between 1 and 9 according the the relative importance of criterion $i$ and criterion $j$.
\end{itemize}

@@

In this project, the 9 software qualities mentioned above are the criteria ($m = 9$), while 29 software packages ($n = 29$) are compared for each of the $m$ criteria. The software are evaluated with the grading template in Appendix \ref{ap_grading_template} and a subjective score from one to ten is given for each quality for each package. To convert the results into pair-wise scores, we apply the following steps: for each quality, for a pair of packages $i$ and $j$, such that $score_i >= score_j$, the pairwise comparison result of $i$ versus $j$ is converted from $min((score_i - score_j) + 1, 9)$.

>>>>

@@

In this section, we introduce the relevant software categories (Section \ref{sec_software_categories}). We also cover the software quality definitions (Section \ref{sec_software_quality}) and an overview of the AHP (Section \ref{sec_AHP}).

\section{Software Categories}
\label{sec_software_categories}
We target specific software categories to narrow down the scope when selecting software packages for measuring. One way to categorize them is grouping by functions, such as analyzing the scope for the MI software (Section \ref{sec_scope}), which requires specific domain knowledge. In this section, we discuss three common software categories that we can apply to all SC domains: Open source software (OSS), freeware, and commercial software.

@@

	\item \textbf{Correctness \& Verifiability} A program is correct if it behaves according to its stated specifications. Verifiability is the extent to which a set of tests can be written and executed, to demonstrate that the delivered system meets the specification \cite{GhezziEtAl2003}.

@@

For a project with $ m $ criteria, we can use an $m\times m$ matrix $A$ to record the relative importance between factors. When comparing criterion $i$ and criterion $j$, the value of $A_{ij}$ is decided as follows, and the value of $A_{ji}$ is $1/A_{ij}$ \cite{Saaty1990},
\begin{itemize}
	\item $A_{ij} = 1$ if criterion $i$ and criterion $j$ are equally important;
	\item $A_{ij} = 9$ if criterion $i$ is extremely more important than criterion $j$;
	\item $A_{ij}$ equals to an integer value between 1 and 9 according the the relative importance of criterion $i$ and criterion $j$.
\end{itemize}

@@

In this project, the 9 software qualities mentioned above are the criteria ($m = 9$), while 29 software packages ($n = 29$) are compared for each of the $m$ criteria. The software are evaluated with the grading template in Appendix \ref{ap_grading_template} and a subjective score from one to ten is given for each quality for each package. For each quality, for a pair of packages $i$ and $j$, such that $score_i >= score_j$, the difference between two scores is $diff_{ij} = score_i - score_j$. The relationship between $A_{ij} = 1$ and $diff_{ij}$ is as follows:
\begin{itemize}
\item $A_{ij} = 1$ and $diff_{ij} = 0$ when criterion $i$ and criterion $j$ are equally important;
\item $A_{ij}$ increases when $diff_{ij}$ increases;
\item $A_{ij} = 9$ and $diff_{ij} = 9$ when criterion $i$ is extremely more important than criterion $j$.
\end{itemize}
Thus, we approximate the pairwise comparison result of $i$ versus $j$ by the following equation:
\begin{equation}
A_{ij} = min(score_i - score_j + 1, 9)
\end{equation}
